{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-06-13 Notebook LaTEX/Momentum Accelerations/main.tex
manually merged fuck it
OcO, sanity check

        \end{observation}
        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
        It goes over the full context and history for this particular variant of gradient acceleration method. 
        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient.

        \begin{proposition}
            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$, we derive the following algorithm: 
            \begin{align*}
            \end{align*}

@@

@@

            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t - 1)/ L$ is one of the options. 

>>>>

        \end{observation}
        We advise the reader to read the Biliography notes by Ryu \cite[chapter 12]{ryu_large-scale_2022} of his book. 
        It goes over the full context and history for this particular variant of gradient acceleration method. 
        As the time of composing this notes, the writer is still reading on the topic of accelerated gradient. 
        \begin{proposition}
            With $\eta_t, \tilde \eta_t$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} where $\eta_{t + 1} = \tilde \eta_{t + 1} = (t - 1)/L$, we derive the following algorithm: 
                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t), 
                z_{t + 1} &= y_t - L^{-1} \nabla f(y_t), 
                y_{t + 1} &= 
                    \frac{2}{t + 3}
                \right)x_{t +1} + 
                    1 - \frac{2}{t + 3}
                \right)z_{t + 1}. 

@@

        \begin{observation}
            Observe that this is the same algorithm as stated in Ryu's book but with an alternative choice of indexing for $y_t$ and initial condition. 
        \end{observation}

@@

            To satisfy the equality, reader should verify that $\eta_{t + 1} = (t)/ L$ is one of the options. 
